\documentclass[a4paper,11pt]{article}

%======================================================================
%	PACKAGES & FONTS (Organic Handwriting Style - Inconspicuous)
%======================================================================
\usepackage{fontspec}
\usepackage{polyglossia}
\setmainlanguage{greek}
\setotherlanguage{english}

% Use Mynerve for everything - uniform organic look
\setmainfont[
    Path = fonts/mynerve/,
    Extension = .ttf,
    UprightFont = Mynerve-Regular,
    BoldFont = Mynerve-Regular,
    ItalicFont = Mynerve-Regular,
    BoldItalicFont = Mynerve-Regular,
    AutoFakeBold = 2.5 % Heavier stroke for "marker" effect
]{Mynerve-Regular}

\setsansfont[
    Path = fonts/mynerve/,
    Extension = .ttf,
    UprightFont = Mynerve-Regular,
    BoldFont = Mynerve-Regular,
    ItalicFont = Mynerve-Regular,
    BoldItalicFont = Mynerve-Regular,
    AutoFakeBold = 1.5
]{Mynerve-Regular}

\setmonofont[
    Path = fonts/mynerve/,
    Extension = .ttf,
    UprightFont = Mynerve-Regular,
    BoldFont = Mynerve-Regular,
    ItalicFont = Mynerve-Regular,
    BoldItalicFont = Mynerve-Regular,
    AutoFakeBold = 1.5
]{Mynerve-Regular}

\newfontfamily\greekfont[
    Path = fonts/mynerve/,
    Extension = .ttf,
    UprightFont = Mynerve-Regular,
    BoldFont = Mynerve-Regular,
    ItalicFont = Mynerve-Regular,
    BoldItalicFont = Mynerve-Regular,
    AutoFakeBold = 1.5
]{Mynerve-Regular}

% ═══════════════════════════════════════════════════════════════
% LUA RANDOMIZATION (Organic Flow)
% ═══════════════════════════════════════════════════════════════
\directlua{
    local glyph_id = node.id("glyph")
    local literal_id = node.id("pdf_literal")
    if not literal_id then literal_id = node.id("whatsit") end
    local nut = node.direct
    local new_node = nut.new
    local getid = nut.getid
    local getnext = nut.getnext
    local setfield = nut.setfield
    local insert_before = nut.insert_before
    local insert_after = nut.insert_after
    local to_direct = nut.todirect
    math.randomseed(os.time())
    function randomize_text(head)
        local head_nut = to_direct(head)
        local current = head_nut
        while current do
            local next_node = getnext(current)
            if getid(current) == glyph_id then
                -- Subtle rotation
                local ang = math.rad(math.random(-15, 15) / 20.0)
                local c, s = math.cos(ang), math.sin(ang)
                local s_start = string.format("q \%.5f \%.5f \%.5f \%.5f 0 0 cm", c, s, -s, c)
                
                local n_start = new_node(literal_id)
                setfield(n_start, "data", s_start)
                local n_end = new_node(literal_id)
                setfield(n_end, "data", "Q")
                
                head_nut = insert_before(head_nut, current, n_start)
                insert_after(head_nut, current, n_end)
                
                -- Baseline jitter (Natural unevenness)
                local jitter_y = math.random(-3000, 3000)
                nut.sety_offset(current, (nut.gety_offset(current) or 0) + jitter_y)
            end
            current = next_node
        end
        return nut.tonode(head_nut)
    end
    luatexbase.add_to_callback("pre_linebreak_filter", randomize_text, "randomize_text")
    luatexbase.add_to_callback("hpack_filter", randomize_text, "randomize_text_hpack")
}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{multicol}
\usepackage[top=0.3cm, bottom=0.3cm, left=0.3cm, right=0.3cm, footskip=0cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tikz}

% Colors - Blue Ink look
\definecolor{inkcolor}{RGB}{0, 10, 60} 
\color{inkcolor}

% Layout Settings
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlength{\columnsep}{0.4cm}
\setlength{\columnseprule}{0.1pt} % Subtle line between columns
\renewcommand{\columnseprulecolor}{\color{inkcolor!20}} % Very faint sep

\linespread{0.95}

% Custom Section Header - Looks like underlined handwriting
\newcommand{\handsection}[1]{%
    \vspace{6pt}
    \begingroup
    \fontsize{10}{11}\selectfont\bfseries #1
    \endgroup
    \par\vspace{2pt}
    \hrule height 0.5pt width 100\% \relax
    \vspace{2pt}
}

% Customize lists to look like doodles
\setlist[itemize]{label={--}, leftmargin=8pt, itemsep=0pt, topsep=1pt, parsep=0pt}
\setlist[enumerate]{label={\arabic*.}, leftmargin=10pt, itemsep=0pt, topsep=1pt, parsep=0pt}

\begin{document}
\pagestyle{empty}
\fontsize{8.5}{9.5}\selectfont

\begin{multicols*}{3}

% ---------------------------------------------------------
\handsection{1. Αξιολόγηση \& Μετρικές}
\textbf{Confusion Matrix:} Acc=$\frac{TP+TN}{N}$ | Prec=$\frac{TP}{TP+FP}$ \\
Rec=$\frac{TP}{TP+FN}$ | Spec=$\frac{TN}{TN+FP}$ | $F1 = \frac{2PR}{P+R}$. \\
\textbf{Medical Bayes:} $P(Diseas|+) = \frac{Sens \cdot Prev}{Sens \cdot Prev + (1-Spec)(1-Prev)}$. \\
\textbf{Errors:} $MSE = \frac{1}{N}\sum(y-\hat{y})^2$. $R^2 = 1 - \frac{RSS}{TSS}$. \\
\textbf{Bias-Var:} $Err = Bias^2 + Var + Noise$. \\
$\bullet$ High Bias $\to$ Underfit (Simple). $\bullet$ High Var $\to$ Overfit (Complex). \\
\textbf{ROC/AUC:} Plot TPR vs FPR. Random=0.5, Perfect=1. \\
\textbf{Cross-Val:} k-Fold (Low Bias/Var est), Hold-out (Fast).

% ---------------------------------------------------------
\handsection{2. Probabilities \& Info}
\textbf{Bayes:} $P(h|d) \propto P(d|h)P(h)$ (Post~Lik~Prior). \\
\textbf{Bayes Risk:} Choose action w/ min exp. loss. \\
\textbf{Gauss:} $\mathcal{N} \sim |\Sigma|^{-1/2} e^{-\frac{1}{2}(x-\mu)^T \Sigma^{-1} (x-\mu)}$. \\
MLE: $\hat{\mu} = \bar{x}$, $\hat{\sigma}^2 = \frac{1}{N}\sum(x-\mu)^2$ (Biased). Unbiased: divide $N-1$. \\
\textbf{Entropy:} $H(P) = -\sum P \log P$. Max at uniform. \\
\textbf{KL Div:} $D_{KL} = \sum P \ln \frac{P}{Q}$. \textbf{CrossEnt:} $H(P,Q) = H(P)+D_{KL}$. \\
\textbf{MLE:} $\max \sum \ln P(x|\theta)$. $\nabla \ln L = 0$.

% ---------------------------------------------------------
\handsection{3. Γραμμικά Μοντέλα}
\textbf{LinReg:} $w=(X^TX)^{-1}X^Ty$. ($O(N^3)$). \\
\textbf{LogReg:} $P = \sigma(w^Tx) = \frac{1}{1+e^{-z}}$. Convex Loss. \\
$\sigma' = \sigma(1-\sigma)$. Update: $w \leftarrow w + \eta(y-\hat{y})x$. \\
\textbf{LDA:} Max Sep $J(w) = \frac{w^T S_B w}{w^T S_W w}$. \\
$S_B=(m_2-m_1)(m_2-m_1)^T$. $S_W=\sum S_i$. \\
Opt: $w \propto S_W^{-1}(m_2-m_1)$. Assumes equal $\Sigma$. \\
\textbf{Geometry:} Hyperplane $w^Tx+w_0=0$. \\
Dist $r = y(x)/||w||$. $w \perp$ surface. \\
\textbf{Regularization (Shrinkage):} \\
L1 (Lasso): $\lambda|w|$ (Sparsity/Selection). \\
L2 (Ridge): $\lambda w^2$ (Small weights).

% ---------------------------------------------------------
\handsection{4. SVM \& Kernels}
\textbf{Primal:} $\min \frac{1}{2}||w||^2 + C \sum \xi_i$ s.t. $y_i(w^Tx_i+b) \ge 1-\xi_i$. \\
\textbf{Convex:} Global minimum guaranteed. \\
\textbf{Support Vectors:} Points on margin ($y(\cdot)=1$) or errors. Only these affect $w$. \\
\textbf{Margin:} $2/||w||$. Larger C $\to$ Harder (Sm margin). \\
\textbf{Slacks $\xi$:} 0 (correct), $0\!<\!\xi\!<\!1$ (margin vio), $\xi \!>\! 1$ (error). \\
\textbf{Kernel Trick:} $x^T z \to K(x,z)$. Implicit high dim. \\
$\bullet$ Poly: $(x^T z + c)^d$. Dim $\approx d$-order terms. \\
$\bullet$ RBF: $e^{-\gamma||x-z||^2}$. Dim $\infty$. (Taylor exp). \\
\textbf{Geometry:} Max margin boundary is $\perp$ bisector of closest points from classes.

% ---------------------------------------------------------
\handsection{5. Neural Networks}
\textbf{Non-Convex:} Local optima possible. \\
\textbf{Unit:} $z = \sum w_i x_i + b \to a = g(z)$. \\
\textbf{Activ:} ReLU $\max(0,z)$ (Fast, no vanish grad). \\
Sigmoid (0,1), Tanh (-1,1) (Sat at limits). \\
\textbf{Softmax:} $y_k = e^{z_k}/\sum e^{z_j}$. For Multi-class. \\
\textbf{Forward:} $Z^{[l]} = W^{[l]}A^{[l-1]}+b^{[l]}, A^{[l]}=g(Z^{[l]})$. \\
\textbf{Backprop:} Chain rule $\frac{\partial J}{\partial W}$. \\
$\delta^L = (a^L-y)$, $\delta^l = (W^{l+1})^T \delta^{l+1} \cdot g'(z^l)$. \\
$\partial J / \partial W^l = \delta^l (a^{l-1})^T$. \\
\textbf{Params:} FC: $(N_{in}+1)N_{out}$. \\
\textbf{CNN:} $Out = \lfloor \frac{W-K+2P}{S} \rfloor + 1$. \\
Params: $F \times F \times C_{in} \times C_{out} + C_{out}$. \\
\textbf{Optim:} SGD (Noisy), Batch (Slow), Mini-batch. \\
Momentum (Velocity), Adam (Adapt LR).

% ---------------------------------------------------------
\handsection{6. Ensembles}
\textbf{Bagging:} Bootstrap (replace) + Parallel Models. \\
Reduces \textbf{Variance}. Ex: Random Forest. \\
\textbf{Random Forest:} Bagging + Feature subset ($\sqrt{p}$). \\
Decorrelates trees -> Better reduction of var. \\
\textbf{Boosting:} Sequential. Fix prev errors. \\
Reduces \textbf{Bias} (and Var). Ex: AdaBoost, XGB. \\
\textbf{AdaBoost:} Weights $\alpha_t = \frac{1}{2}\ln \frac{1-\epsilon}{\epsilon}$. \\
Data weights $D_{t+1} \propto D_t e^{-\alpha y \hat{y}}$ (Focus Hard). \\
\textbf{Trees:} Split: Max InfoGain ($H_{pre} - H_{post}$). \\
Entropy $-\sum p \log p$, Gini $1-\sum p^2$.

% ---------------------------------------------------------
\handsection{7. Unsupervised \& PCA}
\textbf{PCA:} Max Variance directions (Ortho). \\
1. Center ($x-\mu$). 2. Cov $\Sigma = \frac{1}{N}X^TX$. 3. Eigendecomp $U\Lambda U^T$. \\
Proj $z = U_k^T x$. Var ratio $\sum_1^k \lambda_i / \sum \lambda_{all}$. \\
Included '1' feature doesn't change PCA (const var=0). \\
\textbf{K-Means:} Iterate: Assign closest, Update centroids. \\
Converges finite steps. Spherical clusters. Sensitive to K/Init. \\
\textbf{GMM:} Soft K-means. Probabilistic ($\pi, \mu, \Sigma$). \\
\textbf{EM Algo:} Max Likelihood (local max). \\
E-step: Calc responsibilities $\gamma$. M-step: Update params. \\
\textbf{DBSCAN:} Density. core/border/noise. Args: eps, minPts. \\
\textbf{Hierarchical:} Agglomerative. \\
Linkage: Single (min dist), Complete (max), Avg. \\
\textbf{Silhouette:} $\frac{b-a}{\max(a,b)}$. +1 Good, 0 Border, -1 Wrong.

% ---------------------------------------------------------
\handsection{8. KNN \& Dim Reduction}
\textbf{KNN:} Lazy. Distances ($L_2$). \\
Small k $\to$ High Var (Noise). Large k $\to$ High Bias (Smooth). \\
\textbf{Curse of Dim:} Vol grows exp. Points equidistant. \\
Need exp data. Solutions: PCA, Feature Sel.

% ---------------------------------------------------------
\handsection{9. True/False Exam Bible (1/2)}
\textit{-- SVM Objective:} Convex Quatratic (Global Min). \\
\textit{-- NN Objective:} Non-Convex (Local Min). \\
\textit{-- EM Algo:} Maximizes Likelihood (Local Max). \\
\textit{-- K-Means:} Loss decreases monotonically. Converges. \\
\textit{-- RBF Feature Space:} Infinite dimensional. \\
\textit{-- PCA:} Adding const feature -> No change. \\
\textit{-- Perceptron:} Oscillates if not lin sep. \\
\textit{-- Hard Margin SVM:} Requires lin sep. \\
\textit{-- Bootstrapping:} Sampling WITH replacement.

% ---------------------------------------------------------
\handsection{10. True/False Exam Bible (2/2)}
\textit{-- L1 Reg:} Sparsity (Feat Sel). L2: Small Weights. \\
\textit{-- Bias-Var:} 1-NN (High Var), K-NN (High Bias). \\
\textit{-- Kernel Trick:} $w$ is lin comb of data (Representer). \\
\textit{-- Softmax:} Used for Multi-class Output. \\
\textit{-- Linear Activ in Hidden:} Collapse to linear model. \\
\textit{-- Generative:} Naive Bayes, GMM, LDA. \\
\textit{-- Discriminative:} LogReg, SVM, NN, KNN. \\
\textit{-- Decision Trees:} Pruning reduces overfitting.

% ---------------------------------------------------------
\handsection{11. Quick Math/Formulas}
\textbf{Logarithms:} $\ln(xy)=\ln x+\ln y$, $\ln(e^x)=x$. \\
\textbf{Derivatives:} $\frac{d}{dx} \sigma(x) = \sigma(1-\sigma)$. \\
\textbf{Matrix:} $(AB)^T = B^T A^T$. $\nabla_x w^Tx = w$. \\
$\nabla_x x^TAx = (A+A^T)x$. \\
\textbf{Distances:} $L_1$ Manhattan $\sum|x|$, $L_2$ Euclidean $\sqrt{\sum x^2}$. \\
\textbf{Eigen:} $Av = \lambda v$. $\det(A-\lambda I)=0$. \\
\textbf{Normal:} $68\%$ ($1\sigma$), $95\%$ ($2\sigma$), $99.7\%$ ($3\sigma$).

% ---------------------------------------------------------
\handsection{12. Algorithm Summary}
\textbf{Naive Bayes:} $P(y|x) \propto P(y) \prod P(x_i|y)$. Fast, High Bias. \\
\textbf{LogReg:} Linear boundary. Intepretable. P-values. \\
\textbf{SVM:} Max Margin. Robust. Kernels $\to$ Non-Lin. \\
\textbf{DT:} Non-parametric. Interp. Orthogonal splits. \\
\textbf{RF/GBM:} Black-box. High Acc. Robust. \\
\textbf{NN:} Univ approx. Needs data/compute. Non-convex. \\
\textbf{K-Means:} Simple. Scalable. Convex clusters only.

\end{multicols*}
\end{document}
